\chapter{Proofreaders}
Proofreaders should pay attention to spelling, grammar, style etc.  Please refer to the Generic Style Rules and the house rules listed in \sectref{sec:houserules}.

Proofreaders can choose their preferred way of working. Pdf comments, scanned comments on printout, or lists of errors with page numbers are all acceptable.

\laundrybox{Proofreading text}{ 
\laundryitem All floats are referenced.
\laundryitem All examples are referenced.
\laundryitem The guidelines adhered to.
\laundryitem British or American spelling is consistent per author.
\laundryitem ``Section'', ``Table'', or ``Figure'' in cross-references are capitalized.
\laundryitem Spacing after punctuation and parentheses is correct.
\laundryitem Parentheses and brackets in examples are not italicized. 
\laundryitem Subscripts in examples are not italicized.
\laundryitem Footnotemarks in examples are not italicized.
\laundryitem Parentheses are set correctly for all references.
\laundryitem No double parentheses for citations in a parenthesized environment.
\laundryitem Examples which are full sentences finish with punctuation in both source and translation.
\laundryitem Examples which are not full sentences do not have a punctuation mark in source or translation.
\laundryitem Alignment of glossed examples is correct.
\laundryitem All examples have information about language and source. 
}


\laundrybox{Proofreading bibliography}{
\laundryitem All first names are given in full unless the person prefers to use initials.
\laundryitem No double city names in places of publication.
\laundryitem \emph{et al.} not used in bibliography
\laundryitem Subtitles are capitalized
\laundryitem Proper nouns are capitalized
\laundryitem German nouns are capitalized
\laundryitem No extraneous information in bibliography
\laundryitem Series title and series number are typeset correctly
} 





